---
title: "My document"
---


First Extract the Data from the World Bank API using an R Script.

**Extract**

```{r}
source("load_worldbank.R")
```


**Transform**

Use Python for Data Engineering and Data Cleaning.

```{python}
exec(open("transform_merge_data_.py").read())
```

**Load**
```{r}
merged_mpd <- read.csv("merged_mpd.csv")

```

Country and Partynames,



| Country | New Radical Right Party |
|---------|-------------------------|
| Denmark | Danish People's Party   |
| France  | National Front          |
| Germany | Alternative for Germany |
| Hungary | Fidesz                  |
| Italy   | Brothers of Italy       |
| Italy   | Northern League         |
| Norway  | Progress Party          |
| Poland  | Law and Justice Party   |
| Sweden  | Sweden Democrats        |

Create Dummy Variables for each New Radical Right Party.

```{r}
## Dummy Variable for National Front, France's NRR Party.
merged_mpd$nf_dummy <- ifelse(merged_mpd$partyname == "National Front", 1, 0)
```

```{r}
## Dummy Variable for Alternative for Germany, Germany's NRR Party.
merged_mpd$afd <- ifelse(merged_mpd$partyname == "Alternative for Germany", 1, 0)
```

```{r}
## Dummy Variable for Voice(Vox), Spain's NRR Party.
merged_mpd$spain_dummy <- ifelse(merged_mpd$partyname == "Voice", 1, 0)
```

```{r}
## Dummy Variable for Danish People's Party, Denmark's NRR Party.
merged_mpd$dk_dummy <- ifelse(merged_mpd$partyname == "Danish People’s Party", 1, 0)
```

```{r}
## Dummy Variable for Sweden Democrats, Sweden's NRR Party.
merged_mpd$sd_dummy <- ifelse(merged_mpd$partyname == "Sweden Democrats", 1, 0)
```

```{r}
## Dummy Variable for Law and Justice, Poland's NRR Party.
merged_mpd$pd_dummy <- ifelse(merged_mpd$partyname == "Law and Justice", 1, 0)
```

```{r}
## Dummy Variable for Progress Party, Norway's NRR Party.
merged_mpd$pp_dummy <- ifelse(merged_mpd$partyname == "Progress Party", 1, 0)
```

```{r}
## Italy has Two New Radical Right Parties,  Brothers of Italy is the Party of the current far-right Prime Minister, Meloni but the Northern League is also a Coaltion Party and has been aroudn longer..
merged_mpd$brothers_of_italy <- ifelse(merged_mpd$partyname == "Brothers of Italy", 1, 0)
merged_mpd$nord_league <- ifelse(merged_mpd$partyname == "Northern League", 1, 0)
```

```{r}
## Fidesz has had multiple Coaltions with different Parties, so a dummy value for Each Coalition name. This is relevant as Fidesz started off as a Classcially Liberal Party but has since moved to the Far-Right. fidesz_hdfa is the current Coalition Party of Fidesz and is the Far-Right Party used as comparsion against their fellow NRR counterparts.
merged_mpd$fidesz_cdp <- ifelse(merged_mpd$partyname == "Alliance of Federation of Young Democrats - Hungarian Civic Union - Christian Democratic People's Party", 1, 0)
merged_mpd$fidesz_hdfa <- ifelse(merged_mpd$partyname == "Federation of Young Democrats - Hungarian Civic Party - Hungarian Democratic Forum- Alliance", 1, 0)
merged_mpd$fidesz_ <- ifelse(merged_mpd$partyname == "Federation of Young Democrats", 1, 0)
```


```{r}
library(lme4)   
```

Running a Regression Model for each NRR Party.
##Hypothesis 1
Hypothesis 1:NRR Parties shift their Economic positions during rates of higher unemployment or to match European sentiments.


First lets look at the welfare positions of all NRR parties
The welfare variable measures how pro-welfare, a political party is based on their manifestos. The higher the number, the more pro-welfare the party is. The lower the number, the more anti-welfare the party is.

##Welfare
```{r}
library(stargazer)
nrr_welfare <-(lm(welfare ~ nf_dummy + afd + spain_dummy + dk_dummy + sd_dummy + pd_dummy + pp_dummy + brothers_of_italy + nord_league + fidesz_hdfa, data = merged_mpd))
party_names <- c("National Front", "Alternative for Germany", "Voice", "Danish People's Party",
                 "Sweden Democrats", "Law and Justice", "Progress Party", "Brothers of Italy",
                 "Northern League", "Fidesz - HDFa")
 stargazer(nrr_welfare, type = "text", title = "Welfare Regression",
          covariate.labels = party_names)                
```


It appears that only as a whole many NRR parties have an inverse relationship with Pro-Welfare policies. National Front for example has tried to shift towards a Welfare Chauvinist position but overall they seem anti-welfare.


Let's try one multi-level regression to see if varies accross coderyear and add unemployment rates to see if there is a relationship between High  Unemployment and welfare positions.
The Coderyear refers to the year the manifesto was coded.

```{r}
nrr_welfare_unemployment_multi_level <- lmer(welfare ~ nf_dummy + afd + spain_dummy + dk_dummy + sd_dummy + pd_dummy + pp_dummy + brothers_of_italy + nord_league + fidesz_hdfa +SL.UEM.TOTL.ZS+(1 | coderyear), data = merged_mpd)
summary(nrr_welfare_unemployment_multi_level)
```

As a whole it also, seems that there actually is a Inverse relationship of unemployment and Political parties becoming more pro-welfare. So, we can overal reject that NRR parties become more pro-welfare during a crisis.

Among Individual parties, National Front and AfD have a positive correlation with welfare policies during higher unemployment rates. However, their t-value is overall negative. The only NRR party wth a positive t-value is the sd_dmm which is the Swedish Democrats.

##Market Economy

This regression below tests suppor for Market Economy with markeco variable. I have also added a E036 variable which is a pro-free-market varabile from EVS, measuring European survey support Privatiziation

```{r}
markeco_evs<- lmer(markeco ~ nf_dummy + afd + spain_dummy + dk_dummy + sd_dummy + pd_dummy + pp_dummy + brothers_of_italy + nord_league + fidesz_hdfa +SL.UEM.TOTL.ZS+(1 | coderyear), data = merged_mpd)
summary(markeco_evs)
```

The T values of most parties except for dk_dummy(Denmark), sd_dummy(Sweden) and pp_dummy(Nirway), are postive , showing that most NRR parties are extremely pro-free_market.

The correlation of Fixed Effects, shows that Afd and National Front both have higher correlations of supporting more free-market policies during higher rates of unemployment. This is interesting as both parties have tried to shift towards a more pro-welfare position.

For the Scandinavian countries, Denmark,Sweden and Norway, only Sweden is shown to have a negative Cross-level interaction with unemployment and support for free-market policies. Overall it seems that NRR parties do not shift their economic positions to the center during increased time_periods of unemployment. It even seems that for NRR parties, increased unemployment means more support for free-market policies, more privatization to address the issue.

##European Values Survey

Now I want to see if NRR parties shift their positions to match European sentiments. I will use the E036 variable from the European Values Survey, which measures support for privatization. The higher the number, the more support for privatization.



```{r}
markeco_evs<- lmer(markeco ~ nf_dummy + afd + spain_dummy + dk_dummy + sd_dummy + pd_dummy + pp_dummy + brothers_of_italy + nord_league + fidesz_hdfa +E036+(1 |coderyear), data = merged_mpd)
summary(markeco_evs)
```

There seems to be an overall wea relationship European support for privatization and NRR parties. The Cross Correlation among individual NRR parties shows very weak levels of correlation. 



Now let's try looking at the EVS Value for welfare, E037, the higher the number , the more a survey respondent supports Government providing welfare assitance. 

```{r}
welfare_evs<- lmer(welfare ~ nf_dummy + afd + spain_dummy + dk_dummy + sd_dummy + pd_dummy + pp_dummy + brothers_of_italy + nord_league + fidesz_hdfa +E037+(1 |coderyear), data = merged_mpd)
summary(welfare_evs)
```

Overall, there is a Negative Correlation in Polittical Parties becoming more pro-welfare and Europeans being more Pro-welfare at the same time. It's an inverse relationship.


Hypopthesis 2: NRR parties shift their stance on immigration during higher migration rates. They also adopt anti-mulitcultural policies due to European sentiments.

```{r}
immigration<- lmer(per601_2 ~ nf_dummy + afd + spain_dummy + dk_dummy + sd_dummy + pd_dummy + pp_dummy + brothers_of_italy + nord_league + fidesz_hdfa+SM.POP.NETM+(1 |coderyear), data = merged_mpd)
summary(immigration)
```

Swedish Democrats seem to be the only NRR party that really has a Positive Correlation of Anti-Immigrant policy and Immigration Statisitcs. National Front has a positve weak correlation between migration rates and anit-Immigrant policy.


Now one last model to see if NRR parties adopt anti-multicultural policies during higher migration rates, and if it has relations with European sentiment, by adding the EVS variable G043, measuring anti-multiculturalism attitudes among europeans.
```{r}
anti_muliticultural_model<- lmer(per607_2 ~ nf_dummy + afd + spain_dummy + dk_dummy + sd_dummy + pd_dummy + pp_dummy + brothers_of_italy + nord_league + fidesz_hdfa+SM.POP.NETM+G043+(1 |coderyear), data = merged_mpd)
summary(anti_muliticultural_model)
```

The model overall shows a inverse relationship that Europeans are not as anti-multicultural overall as NRR parties and there is no correlation between NRR parties becoming more anti-multicultural and Europeans becoming more anti-multicultural. Altough there is a small slight correlation between European becoming more anti-multicultural as migration rates increase.

